MSTK: Mesh Toolkit, v 1.1 - DRAFT

### 2004-01-15 docs/MSTK.tex
Switched back to using List_* instead of Set_* since the word Set can mean assign as well as a group

\begin{description}
\item[]\textbf{\textit{Set\_ptr}}: Handle to a Set object

@@

\newpage
\section{MSTK Functional Interface}
\subsection{Sets}

Sets of entities in MSTK are returned as sets of type
\textit{Set\_ptr}. The following are the set operations available in
MSTK:

\begin{description}
\item[]\textbf{\textit{Set\_ptr} Set\_New(\textit{int} inisize):} Create a
new set with an initial size, \textit{inisize}. If \textit{inisize} is
0, the initial size is set to be 10.

\item[]\textbf{\textit{void} Set\_Delete(\textit{Set\_ptr} l):} Delete a set.

\item[]\textbf{\textit{Set\_ptr} Set\_Compress(\textit{Set\_ptr} l):} Compress
a set.  Doing this while an algorithm is iterating through the set can
currently cause problems!! Calling \textbf{Set\_Compress} could change the
pointer for the set due to reallocation.

\item[]\textbf{\textit{Set\_ptr} Set\_Copy(\textit{Set\_ptr} l):} Return a
copy of a set.

\item[]\textbf{\textit{Set\_ptr} Set\_Add(\textit{Set\_ptr} l, \textit{void
  *}entry):} Add an entry to the set. The entry is appended to the end
of the set.

\item[]\textbf{\textit{Set\_ptr} Set\_ChknAdd(\textit{Set\_ptr} l,
\textit{void *}entry):} Add an entry to a set only if it is not already
in the set.

\item[]\textbf{\textit{int} Set\_Rem(\textit{Set\_ptr} l, \textit{void
  *}entry):} Remove an entry from the set. Returns 1 if successful, 0
otherwise.

\item[]\textbf{\textit{int} Set\_Remi(\textit{Set\_ptr} l, \textit{int} i):}
Remove the i'th valid entry in the set. Returns 1 if successful, 0
otherwise.

\item[]\textbf{\textit{int} Set\_Replace(\textit{Set\_ptr} l, \textit{void
  *}entry, \textit{void *}nuentry):} Replace 'entry' with 'nuentry' in
set. Returns 1 if successful, 0 otherwise.

\item[]\textbf{\textit{int} Set\_Replacei(\textit{Set\_ptr} l, \textit{int}
i, void *nuentry):} Replace the i'th valid entry in the set with
'nuentry'. Returns 1 if successful, 0 otherwise.

\item[]\textbf{\textit{int} Set\_Contains(\textit{Set\_ptr} l, void *entry):}
Returns 1 if set contains the entry, 0 otherwise.

\item[]\textbf{\textit{int} Set\_Locate(\textit{Set\_ptr} l, void *entry):}
Returns the positional index of the entry in the set. Returns -1 if
the set does not contain the entry.

\item[]\textbf{\textit{void *}Set\_Entry(\textit{Set\_ptr} l, \textit{int}
i):} Return the i'th valid entry in the set.  Returns a NULL pointer if
the i'th valid entry could not be found.

\item[]\textbf{\textit{void *}Set\_Next\_Entry(\textit{Set\_ptr} l,
\textit{int} *i):} Return the next valid entry in the set. This routine
works like an iterator. To start iterating through the set, set the
iteration index i=0 and call the routine to get the first entry in the
set. Subsequent calls to the routine will iterate through the entries
in the set. The routine will return a NULL to indicate that the end of
the set is reached.

@@

\item[]\textbf{\textit{int} Set\_Num\_Entries(\textit{Set\_ptr} l):} Return
the number of entries in a set
\end{description}

@@

\item[]\textbf{\textit{MVertex\_ptr} MESH\_Next\_Vertex(\textit{Mesh\_ptr}
mesh, \textit{int} *idx):} Returns the next vertex while iterating
through the vertices of the mesh. See the routine \textbf{Set\_Next\_Entry}
above for an explanation of how the iteration works.

\item[]\textbf{\textit{MEdge\_ptr} MESH\_Next\_Edge(\textit{Mesh\_ptr} mesh,
\textit{int} *idx):} Returns the next edge while iterating through the
edges of the mesh. See the routine Set\_Next\_Entry above for an
explanation of how the iteration works.  The routine always returns
NULL for reduced representations.

\item[]\textbf{\textit{MFace\_ptr} MESH\_Next\_Face(\textit{Mesh\_ptr} mesh,
\textit{int} *idx):} Returns the next face while iterating through the
faces of the mesh. See the routine \textbf{Set\_Next\_Entry} above for
an explanation of how the iteration works.  Only faces explicitly
represented in the mesh are returned for reduced representation (See
explanation for \textbf{MESH\_Num\_Faces}).

@@

\item[]\textbf{\textit{Set\_ptr} MV\_AdjVertices(\textit{MVertex\_ptr}
mvertex):} Set of adjacent or edge connected neighboring vertices of vertex.

\item[]\textbf{\textit{Set\_ptr} MV\_Edges(\textit{MVertex\_ptr} mvertex):}
Set of edges connected to the vertex.

\item[]\textbf{\textit{Set\_ptr} MV\_Faces(\textit{MVertex\_ptr} mvertex):}
Set of faces connected to the vertex.

\item[]\textbf{\textit{Set\_ptr} MV\_Regions(\textit{MVertex\_ptr} mvertex):}
Set of regions connected to the vertex.
\end{description}

@@

\item[]\textbf{\textit{Set\_ptr} ME\_Faces(\textit{MEdge\_ptr} medge):}
Returns the set of faces using this edge.

\item[]\textbf{\textit{Set\_ptr} ME\_Regions(\textit{MEdge\_ptr} medge):}
Returns the set of regions using this edge.

@@

\item[]\textbf{\textit{Set\_ptr} MF\_Vertices(\textit{MFace\_ptr}
    mface, \textit{int} dir, \textit{MVertex\_ptr} mvert):} Return the
  ordered set of the vertices of the face. The vertices are ordered in
  ccw direction while looking down the face 'normal', if 'dir' is 1
  and in the cw direction, if 'dir' is 0. If 'mvert' is specified, the
  vertex set is reordered so that it is the first vertex (This
  argument will be added soon to the function. For now, omit this
  argument). The behavior of this function can be illustrated using
  Figure~\ref{fig:face_def}. For the face shown in the figure, a
  vertex set with ccw ordering or 'dir' = 1 is ${V_0,V_1,V_2,V_3}$ and
  a vertex set with cw ordering or 'dir' = 0 is ${V_0,V_3,V_2,V_1}$.
  A vertex set with ccw ordering starting with vertex $V_2$ is
  ${V_2,V_3,V_0,V_1}$.

@@

\item[]\textbf{\textit{Set\_ptr} MF\_Edges(\textit{MFace\_ptr} mface,
    \textit{int} dir, \textit{MVertex\_ptr} mvert):} Return the
  ordered set of edges of the face. The edges are ordered in the ccw
  while looking down the face 'normal' if dir is 1 and in the cw if
  dir is 0. If 'mvert' is specified, the edge set is reordered so that
  the first edge in the set contains this vertex. More precisely, if
  'dir' is 1, and the first edge is 'e' used in the face in direction
  'd', then \textbf{ME\_Vertex(e,!d)} = mvert. With reference to
  Figure~\ref{fig:face_def}, the edges of the face in the ccw direction or
  'dir' = 1 are ${E_0,E_1,E_2,E_3}$ and in the opposite dir are
  ${E_3,E_2,E_1,E_0}$. If 'mvert' or the starting vertex is specified
  as $V_2$, the edge set in ccw direction or 'dir' = 1 is
  ${E_2,E_3,E_0,E_1}$ and in the opposite direction is
  ${E_1,E_0,E_3,E_2}$.

\item[]\textbf{\textit{Set\_ptr} MF\_AdjFaces(\textit{MFace\_ptr} mface):}
Set of adacent faces of a face. This operator is relevant only in
planar or surface surface meshes, i.e., for boundary faces not
connected to any regions.

@@

\item[]\textbf{\textit{Set\_ptr} MF\_Regions(\textit{MFace\_ptr} mface):}
Return the set of regions connected to the face. If the face is not
used by any regions, the function returns NULL to indicate that the
set is empty. If not the set may contain one or two regions.

@@

\item[]\textbf{\textit{Set\_ptr} MR\_Vertices(\textit{MRegion\_ptr}
mregion):} Returns the set of vertices of a region. For standard
elements the vertices are ordered as indicated in
Appendix~\ref{app:reg_conventions}. For non-standard elements the set
is unordered.

\item[]\textbf{\textit{Set\_ptr} MR\_Edges(\textit{MRegion\_ptr} mregion):}
Return the \underline{unordered} set of edges of a region.

\item[]\textbf{\textit{Set\_ptr} MR\_Faces(\textit{MRegion\_ptr} mregion):}
Returns the set of faces of a region.

\item[]\textbf{\textit{Set\_ptr} MR\_AdjRegions(\textit{MRegion\_ptr}
mregion):} Returns the set of adjacent regions of a region, i.e.,
regions sharing a face with this region. The set is not ordered.

@@

\item[]\textbf{\textit{void} Set\_Mark(\textit{Set\_ptr} list, \textit{int} mkr):} Mark a set of entities with given marker.

\item[]\textbf{\textit{void} Set\_Unmark(\textit{Set\_ptr} list, \textit{int} mkr):}
Unmark a set of entities with respect to the given marker.

@@

\item[]\textbf{\textit{void} Set\_PrintID(\textit{Set\_ptr} l):} Debugging
utility to print the IDs of the entities in a set.

>>>>

\begin{description}
\item[]\textbf{\textit{List\_ptr}}: Handle to a List object

@@

\newpage
\section{MSTK Functional Interface}
\subsection{List}

Lists of entities in MSTK are returned as sets of type
\textit{List\_ptr}. The following are the set operations available in
MSTK:

\begin{description}
\item[]\textbf{\textit{List\_ptr} List\_New(\textit{int} inisize):} Create a
new set with an initial size, \textit{inisize}. If \textit{inisize} is
0, the initial size is set to be 10.

\item[]\textbf{\textit{void} List\_Delete(\textit{List\_ptr} l):} Delete a set.

\item[]\textbf{\textit{List\_ptr} List\_Compress(\textit{List\_ptr} l):} Compress
a set.  Doing this while an algorithm is iterating through the set can
currently cause problems!! Calling \textbf{List\_Compress} could change the
pointer for the set due to reallocation.

\item[]\textbf{\textit{List\_ptr} List\_Copy(\textit{List\_ptr} l):} Return a
copy of a set.

\item[]\textbf{\textit{List\_ptr} List\_Add(\textit{List\_ptr} l, \textit{void
  *}entry):} Add an entry to the set. The entry is appended to the end
of the set.

\item[]\textbf{\textit{List\_ptr} List\_ChknAdd(\textit{List\_ptr} l,
\textit{void *}entry):} Add an entry to a set only if it is not already
in the set.

\item[]\textbf{\textit{int} List\_Rem(\textit{List\_ptr} l, \textit{void
  *}entry):} Remove an entry from the set. Returns 1 if successful, 0
otherwise.

\item[]\textbf{\textit{int} List\_Remi(\textit{List\_ptr} l, \textit{int} i):}
Remove the i'th valid entry in the set. Returns 1 if successful, 0
otherwise.

\item[]\textbf{\textit{int} List\_Replace(\textit{List\_ptr} l, \textit{void
  *}entry, \textit{void *}nuentry):} Replace 'entry' with 'nuentry' in
set. Returns 1 if successful, 0 otherwise.

\item[]\textbf{\textit{int} List\_Replacei(\textit{List\_ptr} l, \textit{int}
i, void *nuentry):} Replace the i'th valid entry in the set with
'nuentry'. Returns 1 if successful, 0 otherwise.

\item[]\textbf{\textit{int} List\_Contains(\textit{List\_ptr} l, void *entry):}
Returns 1 if set contains the entry, 0 otherwise.

\item[]\textbf{\textit{int} List\_Locate(\textit{List\_ptr} l, void *entry):}
Returns the positional index of the entry in the set. Returns -1 if
the set does not contain the entry.

\item[]\textbf{\textit{void *}List\_Entry(\textit{List\_ptr} l, \textit{int}
i):} Return the i'th valid entry in the set.  Returns a NULL pointer if
the i'th valid entry could not be found.

\item[]\textbf{\textit{void *}List\_Next\_Entry(\textit{List\_ptr} l,
\textit{int} *i):} Return the next valid entry in the set. This routine
works like an iterator. To start iterating through the set, set the
iteration index i=0 and call the routine to get the first entry in the
set. Subsequent calls to the routine will iterate through the entries
in the set. The routine will return a NULL to indicate that the end of
the set is reached.

@@

\item[]\textbf{\textit{int} List\_Num\_Entries(\textit{List\_ptr} l):} Return
the number of entries in a set
\end{description}

@@

\item[]\textbf{\textit{MVertex\_ptr} MESH\_Next\_Vertex(\textit{Mesh\_ptr}
mesh, \textit{int} *idx):} Returns the next vertex while iterating
through the vertices of the mesh. See the routine \textbf{List\_Next\_Entry}
above for an explanation of how the iteration works.

\item[]\textbf{\textit{MEdge\_ptr} MESH\_Next\_Edge(\textit{Mesh\_ptr} mesh,
\textit{int} *idx):} Returns the next edge while iterating through the
edges of the mesh. See the routine List\_Next\_Entry above for an
explanation of how the iteration works.  The routine always returns
NULL for reduced representations.

\item[]\textbf{\textit{MFace\_ptr} MESH\_Next\_Face(\textit{Mesh\_ptr} mesh,
\textit{int} *idx):} Returns the next face while iterating through the
faces of the mesh. See the routine \textbf{List\_Next\_Entry} above for
an explanation of how the iteration works.  Only faces explicitly
represented in the mesh are returned for reduced representation (See
explanation for \textbf{MESH\_Num\_Faces}).

@@

\item[]\textbf{\textit{List\_ptr} MV\_AdjVertices(\textit{MVertex\_ptr}
mvertex):} List of adjacent or edge connected neighboring vertices of vertex.

\item[]\textbf{\textit{List\_ptr} MV\_Edges(\textit{MVertex\_ptr} mvertex):}
List of edges connected to the vertex.

\item[]\textbf{\textit{List\_ptr} MV\_Faces(\textit{MVertex\_ptr} mvertex):}
List of faces connected to the vertex.

\item[]\textbf{\textit{List\_ptr} MV\_Regions(\textit{MVertex\_ptr} mvertex):}
List of regions connected to the vertex.
\end{description}

@@

\item[]\textbf{\textit{List\_ptr} ME\_Faces(\textit{MEdge\_ptr} medge):}
Returns the set of faces using this edge.

\item[]\textbf{\textit{List\_ptr} ME\_Regions(\textit{MEdge\_ptr} medge):}
Returns the set of regions using this edge.

@@

\item[]\textbf{\textit{List\_ptr} MF\_Vertices(\textit{MFace\_ptr}
    mface, \textit{int} dir, \textit{MVertex\_ptr} mvert):} Return the
  ordered set of the vertices of the face. The vertices are ordered in
  ccw direction while looking down the face 'normal', if 'dir' is 1
  and in the cw direction, if 'dir' is 0. If 'mvert' is specified, the
  vertex set is reordered so that it is the first vertex (This
  argument will be added soon to the function. For now, omit this
  argument). The behavior of this function can be illustrated using
  Figure~\ref{fig:face_def}. For the face shown in the figure, a
  vertex set with ccw ordering or 'dir' = 1 is ${V_0,V_1,V_2,V_3}$ and
  a vertex set with cw ordering or 'dir' = 0 is ${V_0,V_3,V_2,V_1}$.
  A vertex set with ccw ordering starting with vertex $V_2$ is
  ${V_2,V_3,V_0,V_1}$.

@@

\item[]\textbf{\textit{List\_ptr} MF\_Edges(\textit{MFace\_ptr} mface,
    \textit{int} dir, \textit{MVertex\_ptr} mvert):} Return the
  ordered set of edges of the face. The edges are ordered in the ccw
  while looking down the face 'normal' if dir is 1 and in the cw if
  dir is 0. If 'mvert' is specified, the edge set is reordered so that
  the first edge in the set contains this vertex. More precisely, if
  'dir' is 1, and the first edge is 'e' used in the face in direction
  'd', then \textbf{ME\_Vertex(e,!d)} = mvert. With reference to
  Figure~\ref{fig:face_def}, the edges of the face in the ccw direction or
  'dir' = 1 are ${E_0,E_1,E_2,E_3}$ and in the opposite dir are
  ${E_3,E_2,E_1,E_0}$. If 'mvert' or the starting vertex is specified
  as $V_2$, the edge set in ccw direction or 'dir' = 1 is
  ${E_2,E_3,E_0,E_1}$ and in the opposite direction is
  ${E_1,E_0,E_3,E_2}$.

\item[]\textbf{\textit{List\_ptr} MF\_AdjFaces(\textit{MFace\_ptr} mface):}
List of adacent faces of a face. This operator is relevant only in
planar or surface surface meshes, i.e., for boundary faces not
connected to any regions.

@@

\item[]\textbf{\textit{List\_ptr} MF\_Regions(\textit{MFace\_ptr} mface):}
Return the set of regions connected to the face. If the face is not
used by any regions, the function returns NULL to indicate that the
set is empty. If not the set may contain one or two regions.

@@

\item[]\textbf{\textit{List\_ptr} MR\_Vertices(\textit{MRegion\_ptr}
mregion):} Returns the set of vertices of a region. For standard
elements the vertices are ordered as indicated in
Appendix~\ref{app:reg_conventions}. For non-standard elements the set
is unordered.

\item[]\textbf{\textit{List\_ptr} MR\_Edges(\textit{MRegion\_ptr} mregion):}
Return the \underline{unordered} set of edges of a region.

\item[]\textbf{\textit{List\_ptr} MR\_Faces(\textit{MRegion\_ptr} mregion):}
Returns the set of faces of a region.

\item[]\textbf{\textit{List\_ptr} MR\_AdjRegions(\textit{MRegion\_ptr}
mregion):} Returns the set of adjacent regions of a region, i.e.,
regions sharing a face with this region. The set is not ordered.

@@

\item[]\textbf{\textit{void} List\_Mark(\textit{List\_ptr} list, \textit{int} mkr):} Mark a set of entities with given marker.

\item[]\textbf{\textit{void} List\_Unmark(\textit{List\_ptr} list, \textit{int} mkr):}
Unmark a set of entities with respect to the given marker.

@@

\item[]\textbf{\textit{void} List\_PrintID(\textit{List\_ptr} l):} Debugging
utility to print the IDs of the entities in a set.
